Fractional anisotropy as a tracer of cosmic voids

### 2014-12-18 cosmic_voids.tex
revisado abstract y primer parrafo de la introduccion

\begin{abstract}
Finding and characterizing voids in the large scale structure of the
universe is an important task in cosmological studies. 
In this paper we present a novel approach to find voids in
cosmological simulations.  
It is based on algorithms that use the tidal and the
velocity shear tensors to define the cosmic web.
Voids are identified using the fractional anisotropy (FA) computed
from the eigenvalues of each web scheme. We define the void boundaries
using a watershed transform based on the local minima of the FA; the
boundaries are regions where the FA is maximized, corresponding to
walls and filaments.  This void definition does not have any free
parameter and does not make any assumption on the shape or structure
of the voids.  We test the method on the Bolshoi simulation and report
on the density and velocity profiles for the voids found using this
new scheme.
\end{abstract}

@@

Since voids where discovered in the first compiled galaxy surveys 
\citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
Kirshner87}, they have been identified, along with the filamentary and 
hierarchically clustered nature of the Cosmic Web, as one of the most 
striking features of the Megaparsec Universe \citep{Bond96}. Nevertheless,
due to the large volume extension of void regions ($\sim 5-10\ \mbox{Mpc} 
h^{-1}$), statistically meaningful catalogues of voids \citep{Pan10, 
Sutter12b, Nadathur14} only have become available after modern large 
galaxy surveys like the two-degree field Galaxy Redshift Survey \citep{
Colless01, Colless03} and the Sloan Digital Sky Survey \citep{York00,
Abazajian03}, thereby triggering a plethora of more refined observational 
and statistical studies of voids throughout the last decade \citep{Hoyle04,
Croton04, Rojas05, Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b, 
Tikhonov07, BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}

>>>>

\begin{abstract}
Finding and characterizing underdense regions (voids) in the large
scale structure of the Universe is an important task in cosmological
studies.  
In this paper we present a novel approach to find voids in
cosmological simulations.  
Our approach is based on algorithms that use the tidal and the
velocity shear tensors to locally define the cosmic web.
Voids are identified using the fractional anisotropy (FA) computed
from the eigenvalues of each web scheme. 
We define the void boundaries using a watershed transform based on the
local minima of the FA and its boundaries as the regions where the FA
is maximized
This void identification technique does not have any free parameters
and does not make any assumption on the shape or structure of the
voids.  
We test the method on the Bolshoi simulation and report on the density
and velo ity profiles for the voids found using this new scheme. 
\end{abstract}

@@

Since voids were found in the first compiled galaxy surveys 
they have been identified as one of the most striking features of the
Cosmic Web \citep{Chincarini75,  Gregory78, Einasto80M, Einasto80N,
  Kirshner81,  Kirshner87, Bond96}. 
However,  due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through  modern galaxy surveys like the two-degree field Galaxy
Redshift Survey \citep{ Colless01, Colless03} and the Sloan Digital
Sky Survey \citep{York00, Abazajian03}.
This advancement generated a great interest to study voids
observationally during the last decade \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.
